Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
take a stab at intro

- What are linguistic communities
  - Linguistic complexity
- Community Conditioned language models
- Latent Community Classifier

We propose to test the following hypotheses:

\begin{hypotheses}
\item Different communities have different levels of linguistic
  complexity

\item LCC works: the communty-specific linguistic features are recognized by CCLM.
\item The layer at which the community embedding is taken into account
  in CCLM influences its perplexity.
\item The layer at which the community embedding is taken into account
  influences the LCC.
\item Correlation between community language complexity and recognisability. (False)
\item Community embedding are correlated with coocurrence of users
  between communities.
% \item Community stability is correlated with language complexity
\end{hypotheses}

@@

Our dataset includes messages from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} messages per month for each month
in the three years between 2015 and 2017. 
We initially selected \num{50} subreddits, 
but excluded four of them from further analysis: 
two which were primarily non-English and two with particularly\jp{quantify?} short average message lengths.
Each community corpus consist of \num{50000} randomly selected messages from the year 2015.

>>>>

TODO: What is a linguistic community.

Broadly construed, we want to investigate two questions.  First, we
are interested in the variation of to what extent are various
communities exhibiting various level of linguistic complexity.

TODO: insert some anecdotes (perhaps some particularly stupid/clever
comments from reddit here.)

It is folklore that certain communities are more complex
linguistically: here we want to quantify this phenomenon.

More precisely, we investigate if this degree of complexity be
captured in a computational model.  For this purpose define various
Community Conditioned Language Models (CCLM for short), which can be
modeled as an estimator $M$ what a given message $m$ is acceptable in
a given community $c$: \(P_M(m \mid c)\).

Second, we want to find out how, and how much, CCLMs can be attuned to
the specificity of communities. We test whether 1. the linguistic
models are correlated with a model of community based only on
co-occurence of users between communities and 2. if latent community
classifiers based on the CCLM can accurately identify that a given message
comes from a given community.

To sum up, we propose to test the following hypotheses:
\begin{hypotheses}
\item Different communities have different levels of linguistic
  complexity
\item The layer at which the community embedding is taken into account
  in CCLM influences its perplexity.
\item CCLM can be used to recognize communities based on
  latent bayesian classification.
\item The layer at which the community embedding is taken into account
  influences CCLM and its associated latent classifier.
  % \item There is a correlation between community language complexity and recognizability.
  % This is more of a justification for studying the latent classifier than a real "user-facing" hypothesis.
\item The model representation of communities are correlated with
  co-ocurrence of users between communities.
% \item Community stability is correlated with language complexity
\end{hypotheses}

@@

Our dataset includes messages from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} messages per month for each month
in the three years between 2015 and 2017. 
We initially selected \num{50} subreddits, 
but excluded four of them from further analysis: 
two because they were primarily non-English and two with particularly\jp{quantify?} short average message lengths.
Each community corpus consist of \num{50000} randomly selected messages from the year 2015.
